Appendix A: Code and supplementary figures for simulation and policy analyis

### 2018-12-07 appendix/appendixA.Rmd
try to cache slow block for travis
fix typo
cache another possibly slow block

```{r pomdp_sims}
set.seed(12345)

@@

```{r overest}
set.seed(12345)
true <- 3 # sigma_g = 0.15, sigma_m = 0
source(system.file("examples/pomdp_overestimates.R", package="sarsop")) # portable example code
pomdp_overest_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
    pomdp_overestimates(transition = .x$transition, 
            model_observation = .x$observation, 
            reward = .x$reward, 
            discount = discount, 
            true_observation = models[[true]]$observation,
            x0 = x0,
            Tmax = Tmax,
            alpha = .y,
            reps = reps)$df %>% 
              mutate(method = "POMDP") # include a column labeling method
           },
           .id = "scenario"
  )
write_csv(pomdp_overest_sims, file.path(log_dir, "pomdp_overest_sims.csv"))
```

>>>>

```{r pomdp_sims, eval=!file.exists(file.path(log_dir, "pomdp_sims.csv"))}

set.seed(12345)

@@

```{r overest, eval = !file.exists(file.path(log_dir, "pomdp_overest_sims.csv"))}
set.seed(12345)
true <- 3 # sigma_g = 0.15, sigma_m = 0
source(system.file("examples/pomdp_overestimates.R", package="sarsop")) # portable example code
pomdp_overest_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
    pomdp_overestimates(transition = .x$transition, 
            model_observation = .x$observation, 
            reward = .x$reward, 
            discount = discount, 
            true_observation = models[[true]]$observation,
            x0 = x0,
            Tmax = Tmax,
            alpha = .y,
            reps = reps)$df %>% 
              mutate(method = "POMDP") # include a column labeling method
           },
           .id = "scenario"
  )
write_csv(pomdp_overest_sims, file.path(log_dir, "pomdp_overest_sims.csv"))
```
